### 2017-09-27 TF-vldb2018/sec-appendix.tex

\noindent
{\textbf{3. Algorithm \kw{PFrag} (Section~\ref{sec-dynamictopk})}}

@@

\revise{
Proofs

}

>>>>

\noindent
{\textbf{2. Algorithm \kw{PFrag} (Section~\ref{sec-dynamictopk})}}

@@

\revise{
We will prove Theorem~\ref{thm-tsim-radius} (1) firstly.
We know that $P\eps \ball{[v, t]}$, and $M_t$ is a match relation for $P$ in $\ball{[v, t]}$.
Since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, 
there must exist a binary relation $M_r$ such that for any $(u, v) \in M_t$, where $u$ is a pattern node and $v$ is the matched data node of $u$ in $\ball{[v, t]}$, 
$(u, v) \in M_r$ holds, where $v$ is the matched data node of $u$ in $\ball{[v, r]}$, \ie $M_t \subset M_r$.
Since $M_t$ is a match relation for $P$ in $\ball{[v, t]}$ and $M_t \subset M_r$, by the definition of graph simulation, then $P\eps \ball{[v, r]}$ and $M_r$ is a match relation for $P$ in $\ball{[v, r]}$.

\vspace{-1ex}	
We will prove Theorem (2) using the lemma below.

\vspace{-2.7ex}
\begin{lemma}
	\label{lemma-innerball}
	For any data graphs $G_1$ and $G_2$, pattern graph $P$. If $G_1$ is a subgraph of $G_2$,
	then $M_1 \subset M_2$, where $M_i$ $(i=1,2)$ is the maximum match relation for $P$ in $G_i$ via graph simulation. 
\end{lemma}
\vspace{-2.5ex}

We next prove the lemma and then use the lemma to prove Theorem~\ref{thm-tsim-radius} (2).

\vspace{-2.3ex}
\stitle{Proofs of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
We know that $G_1$ is a subgraph of $G_2$, and suppose $M_1 \not\subset M_2$.
That is, there exists a pair of nodes $(u, v) \in M_1$, where $u$ is a pattern node 
and $v$ is the matched data node of $u$, but $(u, v) \not\in M_2$.
By the definition of graph simulation, from $(u, v) \in M_1$, we know that for any child node $u'$ of $u$ in $P$,
there exists a child node $v'$ of $v$ in $G_1$ such that $(u', v') \in M_1$.
From $(u, v) \not\in M_2$, we know that there exists a child node $u''$ of $u$ in $P$, 
but there exist no child nodes $v''$ of $v$ in $G_2$, such that $(u'', v'') \eps M_2$.
The process to compute maximum match relations for graph simulation is a recursive process to 
remove invalid matches from the initialized match relations $M$.
Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, so $(u, v)$ is removed from $M_2$.
As $G_1$ is a subgraph of $G_2$, so $(u, v)$ should also be removed from $M_1$, 
such that $(u, v) \not\in M_1$.
This contradicts the assumption that $(u, v) \in M_1$, and we get the lemma proved.
\eop

\vspace{-1.5ex}
By Lemma~\ref{lemma-innerball}, since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, then $M' \subset M$.
By the definition of match graphs, since $M' \subset M$, then $G'_s$ is a subgraph of $G_s$.
}
